---
title: "Could evolution explain differences in functional richness and evenness along species richness gradients? A formal test using multivariate trait simulations"
author: 
date: "2026-02-20"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
<!-- badges: end -->

#### Organization of the repository:\

*Root*\
|\
|-- *data_fish*: data of reef fishes from Morais et al. 2017 - file "UpdatedData_RMorais_et_al_2017.csv".\ 
|-------- The folder 'TACT' hosts the fish phylogenies (from Siqueira et al. 2020), file "Reef_fish_all_combined.trees".\
|-------- The file "Atributos_especies_Atlantico_&_Pacifico_Oriental_2020_04_28.csv" has trait data from Quimbayo et al. 2021.\
|-- *data rodents*:\
|-------- "AppendixS1- Small_mammal_data.csv" = data from Luza et al. 2019. "Mammal_Communities.csv" = data from Figueiredo et al. 2017 ("Localities.csv" and "References.csv" are metadata associated to data of Figueiredo et al. 2017).\
|-------- "limites_integradores_wgs84_v1_2_0" folder with Atlantic forest shapefiles Muylaert et al. 2018.\
|-------- "Penone_et_al_2016_mammal_trait_data_imputed.csv" = mammal trait data from Penone et al. 2016.\
|-------- "Sigmodontinae_413species100Trees.trees" = rodent phylogenies from Upham et al. 2016.\
|-- *Processed data*\
|-------- Basic data to fit models ("image*.RData") for each group. Data of environmental and historical covariates after extraction to survey sites are available in this folder.\
|-- *Output*: files in format 'RData' with parameters of macroevolutionary models fitted to the data (sufix 'simulated*.RData') and Bayesian linear models fitted to FRic and FEve data (sufix "GLM").\
|-------- Figures: folder with figures shown in the main text and supporting information.\
|-- *R*: R scripts used in the analyzes. The codes are numbered from 1 to 15, depicting different steps of analysis.\


<!-- badges: start -->
<!-- badges: end -->

#### This paper was produced using the following software and associated packages:\

```{r pressure, echo=F,warning=F,message=F}

source("R/packages.R")
sessionInfo()


```
